---
title: "ipADMIXTURE_demo"
author: " C. Amornbunchornvej"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ipADMIXTURE_demo} 
  %\VignetteEngine{knitr::knitr}
  \usepackage[utf8]{inputenc}
---

Real-world dataset: Human 27 population data

Step1: running the  ipADMIXTURE using Human 27 population dataset where the number of ancestors K =12. 
```{r}
library(ipADMIXTURE)
# # running area: ipADMIXTURE::human27pop_Qmat[[i]] is a Q matrix with K=i+1
h27pop_obj<-ipADMIXTURE(Qmat=ipADMIXTURE::human27pop_Qmat[[11]], admixRatioThs =0.15)
```

Step2: printing all cluster information in text mode.
```{r}
ipADMIXTURE::printClustersFromLabels(h27pop_obj,human27pop_labels)
```

Step3: plotting admixture ratios and clustering assignment.
```{r}
ipADMIXTURE::plotAdmixClusters(h27pop_obj)
```

Step4: plotting clustering information in treemap plot
```{r}
ipADMIXTURE::plotClusterLeaves(h27pop_obj)
```
Step4: Inferring phylogenetic tree of  clusters based on a list of Q matrices that varies K.
```{r}
#out<-ipADMIXTURE::getPhyloTree(human27pop_Qmat,h27pop_obj$indexClsVec)
plot(out$tree, type = "unrooted")
```
